%% Master CV - Brandon McCray
%% Comprehensive overview of all competencies, experience, and achievements.
%% Use as the master reference when tailoring role-specific CVs (cv/main_<company>.tex).
%%
%% Populated by /setup 2026-07-06 (dates/metrics confirmed by Brandon 2026-07-08),
%% targeted at Applied AI Engineer roles.
%% Compile with: lualatex main_example.tex
%% (pdflatex often fails on modern MiKTeX with fontawesome5 font-expansion errors.)

\documentclass[11pt,letterpaper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}

% Force both first and last name AND section headings to render in moderncv
% blue (color1). Default banking on lualatex+MiKTeX leaves these black, which
% looks inconsistent with the rest of the blue accent scheme.
\renewcommand*{\firstnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\lastnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\sectionstyle}[1]{{\sectionfont\color{color1}#1}}

\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
    pdftitle={Brandon McCray - CV},
    pdfpagemode=FullScreen,
}
\usepackage[scale=0.80]{geometry}
\usepackage{import}

% personal data
\name{Brandon}{McCray}
\address{Seattle, WA}{}{}
\phone[mobile]{206.708.3041}
\email{brandonmccray02@gmail.com}
\extrainfo{\href{https://linkedin.com/in/brandonjmccray}{LinkedIn}, \href{https://github.com/CIVIDISO}{GitHub}}

\begin{document}

\makecvtitle

% ============================================================
%     PROFILE STATEMENT
% ============================================================

\vspace{6pt}
\small{Applied AI engineer who ships LLM systems to production, not prototypes. Sole architect of \textbf{PBOMNI}, a multi-tenant operations platform whose network of eight LLM email agents processes roughly 350 emails and orders a week for four departments --- with a human-correction feedback loop. Completing an M.S.\ in Artificial Intelligence (capstone: PBOMNI). Full-stack depth (React/TypeScript, PostgreSQL/Supabase, Edge Functions) plus the business fluency, from board level to bank branch, to turn messy operational workflows into software people actually use.}

% ============================================================
%     CORE COMPETENCIES
% ============================================================

\section{Core Competencies}
\vspace{1pt}
\begin{itemize}

\item \textbf{LLM Application Engineering}: prompt pipelines for structured-data extraction from unstructured text; human-in-the-loop correction feedback; multi-agent workflow routing; Generative AI \& LLM graduate coursework.

\item \textbf{Full-Stack Development}: TypeScript, React, Tailwind CSS, Progressive Web Apps; Supabase Edge Functions (Deno); REST API integration (DocuSign).

\item \textbf{Databases \& Security}: PostgreSQL with Row Level Security, PL/pgSQL, multi-tenant isolation, audit triggers, idempotent migrations; PostgREST hardening.

\item \textbf{Machine Learning \& Data}: Python, PyTorch, TensorFlow, scikit-learn, Pandas, NumPy; NLP and Computer Vision coursework; Power BI, SQL analytics.

\item \textbf{Infrastructure \& Delivery}: GitHub $\rightarrow$ Vercel CI/CD, AWS, environment management, production release discipline as a solo engineer.

\end{itemize}

% ============================================================
%     PROFESSIONAL EXPERIENCE
% ============================================================

\section{Professional Experience}
\vspace{3pt}
\begin{itemize}

% --- Most Recent Role ---
\item{\cventry{Jul 2024--Present}{Chief Data Officer / Junior Board Member (sole engineer)}{Perfect Blend, LLC}{Bellevue, WA}{}{\vspace{1pt}
\begin{itemize}
    \item Sole technical executive of a specialty agriculture company: own technology strategy, AI roadmap, all software development, and vendor evaluation at board level.
    \item Architected, built, and operate \textbf{PBOMNI}, a multi-tenant AI operations platform (React/TypeScript, Supabase/PostgreSQL, Vercel, DocuSign, PWA) used daily by 10 staff across sales, accounting, quality, and logistics --- replacing manual email-to-spreadsheet and paper workflows and eliminating $\sim$20 hours of manual processing per week.
    \item Built a network of \textbf{8 specialized LLM email agents} (order intake, quality, prebuy, AP, freight, HR, reports) that parse $\sim$350 natural-language business emails and orders per week into structured records routed to workflow queues, with a feedback loop that learns from human corrections.
    \item Shipped full sales-order lifecycle (draft $\rightarrow$ approved $\rightarrow$ fulfilled) and Bill of Lading generation with embedded DocuSign signing, deployed as a touch-optimized PWA on a loading-dock tablet.
    \item Implemented Row Level Security across 18+ PostgreSQL tables with multi-tenant company isolation; revoked anonymous PostgREST access; added audit-trigger logging on all financial records; 48+ idempotent production migrations on a GitHub $\rightarrow$ Vercel CI/CD pipeline.
    \item Debugged to root cause: PostgreSQL RLS $\times$ database-view incompatibility at the PL/pgSQL exception-handling level; OAuth/CORS/iframe security conflicts across DocuSign, Supabase Edge Functions, and React.
    \item Automated state product-compliance registration tracking across multiple U.S. jurisdictions; perform P\&L analysis and multi-dimensional sales analysis informing pricing strategy.
\end{itemize}}}

\vspace{3pt}

% --- Previous Role ---
\item{\cventry{Jun 2023--Jul 2024}{Financial Services Representative}{Bank of America --- Consumer \& Small Business}{Seattle, WA}{}{\vspace{1pt}
\begin{itemize}
    \item Conducted fraud investigation and initial due diligence on flagged consumer accounts; maintained G/L account accuracy and reconciliation.
    \item Generated data-driven client pitch analyses on internal banking platforms; member of the Black Employee Network Group.
\end{itemize}}}

\end{itemize}

% ============================================================
%     EDUCATION
% ============================================================

\section{Education}
\vspace{1pt}
\begin{itemize}

\item{\cventry{2025--2027 (expected)}{M.S.\ in Artificial Intelligence}{Seattle University, School of Science \& Engineering}{Seattle, WA}{}{\vspace{1pt}
Capstone: PBOMNI platform (in production). Coursework: Machine Learning, Advanced ML, AI Systems, Big Data Systems, NLP, Computer Vision, Generative AI \& LLMs, AI Governance, Ethics of AI, Mathematics for AI.
}}

\vspace{3pt}

\item{\cventry{2022--2025}{B.S.\ in Business Administration, Digital Marketing minor}{Central Washington University}{Seattle, WA}{}{\vspace{1pt}
Coursework: Financial Statement Analysis, Econometrics, Futures \& Derivatives, SQL, Python.
}}

\vspace{3pt}

\item{\cventry{2019--2021}{A.A.S.\ in Business --- Dean's List}{Pierce College}{Lakewood, WA}{}{}}

\end{itemize}

% ============================================================
%     CERTIFICATIONS & ADDITIONAL
% ============================================================

\section{Certifications \& Additional}
\vspace{1pt}
\begin{itemize}
\item{\textbf{Google Analytics Certification} --- Google (2025).}
\item{Earlier experience: Youth Counselor, YMCA of Pearl Street, Tacoma, WA --- mentored at-risk youth.}
\item{Interests: astronomy, animation, music production, basketball.}
\end{itemize}

% ============================================================
%     REFERENCES
% ============================================================

\section{References}
\vspace{1pt}
\begin{itemize}
\item{Available upon request.}
\end{itemize}

\end{document}
